---
title: Trends of data contained in XML dumps of the Swiss Register of Plant Protection Products
author: Johannes Ranke
date: Last change 9 October 2025 (rebuilt `r Sys.Date()`)
output:
  rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trends of data contained in XML dumps of the Swiss Register of Plant Protection Products}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = TRUE, message = FALSE}
knitr::opts_chunk$set(tidy = FALSE, cache = FALSE)
options(knitr.kable.NA = '')
library(srppphist)
library(dplyr)
library(knitr)
library(ggplot2)
```

## Trends of numbers of active substances

The figure below shows the number of active substances contained in products
occurring in the Swiss Register of Plant Protection Products over the years 
starting from 2011. Unauthorized products and active substance only contained
in such products are filtered out using the function 
[srppp_xml_product_use_no_authorized](https://agroscope-ch.github.io/srppphist/reference/srppp_xml_product_use_not_authorized.html).

The categories are based on the classification in the register. Each active 
substance can have more than one category, therefore the total number of active
numbers is smaller than the sum of the active substances in each category.

```{r warning = FALSE}
years <- names(srppp_list)
names(years) <- years
actives_by_category <- sapply(years, function(year) {
  sr <- srppp_list[[year]]
  actives_categories <- sr$products |>
    mutate(nonauth = srppp_xml_product_use_not_authorized(name, year, exhaustionDeadline)) |>
    filter(!nonauth) |> 
    left_join(sr$categories, by = "pNbr", relationship = "many-to-many") |>
    select(pNbr, category = category_de) |>
    unique() |>
    left_join(sr$ingredients, by = "pNbr", relationship = "many-to-many") |>
    dplyr::filter(type == "ACTIVE_INGREDIENT") |>
    left_join(sr$substances, by = "pk") |>
    select(pk, category, substance_de) |>
    unique() |>
    arrange(pk, substance_de, category)

  n_actives <- actives_categories |>
    select(pk) |>
    unique() |>
    nrow()

  actives_categories |>
    group_by(category) |>
    summarise(n = n()) |>
    arrange(desc(n))

  n_tibble <- actives_categories |>
    mutate(category = case_when(
      grepl("Herbizid", category) ~ "Herbicides",
      grepl("Fungizid", category) ~ "Fungicides",
      grepl("Insektizid", category) ~ "Insecticides",
      grepl("Saatbeizmittel", category) ~ "Seed dressings",
      grepl("Regulator", category) ~ "PGR",
      grepl("Phytoregulator", category) ~ "PGR", # new in 2024
      grepl("Lebende Organismen", category) ~ "Organisms",
      grepl("Akarizid", category) ~ "Acaricides",
      .default = "Others"
    )) |>
    group_by(category) |>
    summarise(n = n()) |>
    arrange(desc(n))

  n <- n_tibble$n
  names(n) <- n_tibble$category
  n <- c(Total = n_actives, n)
  return(n)
})
kable(actives_by_category)
```

```{r fig.width = 7, fig.height = 5}
#| fig.alt: >
#|   Diagram showing the evolution of the number of active substances per category
#|   over time
actives_by_category_long <- actives_by_category |>
  tibble::as_tibble(rownames = "Category") |>
  tidyr::pivot_longer(cols = where(is.numeric), names_to = "Year", values_to = "Number") |>
  ungroup() |>
  group_by(Category)

actives_by_category_long |>
  ggplot(aes(Year, Number, group = Category, color = Category)) +
  geom_point() +
  geom_line()
```

